---
title       : Introduction to data
description : StatsWithR Lab2

--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:9f04a059fc
## Filtering and Counting

Create a new data frame that includes flights headed to SFO in February, and save 
this data frame as `sfo_feb_flights`. <p>How many flights meet these criteria?<p/>

*** =instructions
- 68 
- 1345
- 2286
- 3563
- 32735

*** =hint
Remember the `|` operator allows you to filter for more than one variable. 

*** =pre_exercise_code
```{r,eval=FALSE}
library(dplyr)
library(ggplot2)

```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again! Look at the data frames dimensions with the `dim()` fucntion."
msg2 <- "Try again! The data frames dimensions can be displayed with the `dim()` fucntion." 
msg3 <- "Try again! Use `dim()` fucntion to display the data frames dimensions."
msg4 <- "Correct! There are 3,563 flights heading to San Francisco."
msg5 <- "Not it! Use `dim()` fucntion to display the data frames dimensions."

test_mc(4, feedback_msgs = c(msg1, msg2, msg3, msg4, msg5))
```
*** =attachments
lab1.Rmd: http://s3.amazonaws.com/assets.datacamp.com/production/course_1126/datasets/student_lab_code_test.Rmd

